---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

WaxTools
======

```{r, echo=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_files/"
)

sysfonts::font_add_google(name = "Fira Sans", family = "fira-sans")
sysfonts::font_add_google(name = "Roboto Slab", family = "roboto-slab")

showtext::showtext_auto()

```

## Overview

`waxtools` is a package that brings together a set of useful day-to-day functions to facilitate work in the field of (mainly) ecology. It offers functions to clean up your datasets, customize your `ggplot2` graphs, check and correct the geometry of sf objects, create nice commented titles to separate scripts, and perform other specific tasks such as calculating cumulative specific richness, reformatting dates into a French format, etc. Thanks to the variety of its functions, `waxtools` can be used efficiently and conveniently in a variety of contexts and projects.


## Installation
```{r, eval=FALSE}
devtools::install_github("waxtiz/waxtools")
```

```{r}
library(waxtools)
```


## Usage

### Match taxons names
find_cd_name allows to use the INPN API to find by fuzzy search a list of taxon names.

```{r}
list_sci_species <- unique(naturalist_df$name)[1:5]
list_sci_species
```
```{r, eval = FALSE}
result <- waxtools::find_cd_nom(list_sci_species)[,1:8]
kableExtra::kable(result)
```

```{r, echo = FALSE}
result <- structure(list(sp = c("Casmerodius albus", "Ardea cinerea", "Alcedo atthis",
"Fulica atra", "Aegithalos caudatus"), id = c(2502L, 2506L, 3571L,
3070L, 4342L), referenceId = c(2504L, 2506L, 3571L, 3070L, 4342L
), parentId = c(NA, 189420L, 188938L, 192644L, 188838L), scientificName = c("Casmerodius albus",
"Ardea cinerea", "Alcedo atthis", "Fulica atra", "Aegithalos caudatus"
), authority = c("(Linnaeus, 1758)", "Linnaeus, 1758", "(Linnaeus, 1758)",
"Linnaeus, 1758", "(Linnaeus, 1758)"), fullName = c("Casmerodius albus (Linnaeus, 1758)",
"Ardea cinerea Linnaeus, 1758", "Alcedo atthis (Linnaeus, 1758)",
"Fulica atra Linnaeus, 1758", "Aegithalos caudatus (Linnaeus, 1758)"
), fullNameHtml = c("<i>Casmerodius albus</i> (Linnaeus, 1758)",
"<i>Ardea cinerea</i> Linnaeus, 1758", "<i>Alcedo atthis</i> (Linnaeus, 1758)",
"<i>Fulica atra</i> Linnaeus, 1758", "<i>Aegithalos caudatus</i> (Linnaeus, 1758)"
)), class = "data.frame", row.names = c(NA, -5L))
kableExtra::kable(result)
```

### Calculate the cumulative taxonomic richness

```{r, cache = TRUE}
library(ggplot2)
library(waxtools)

result <- naturalist_df %>%
        calc_rich_sp("name", "date")

ggplot(result, aes(date, cumulative_richness)) +
  geom_point()

```

### waxtheme
```{r, warning = F, cache = TRUE}
library(ggplot2)
library(waxtools)

ggplot(iris, aes(Sepal.Length, Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "First, a chart title",
       subtitle = "Below, a subtitle",
       caption = "And finally, a caption text.") +
  theme_wax(theme = "wax") +
  scale_color_wax_d()
```

wax_theme uses by default the R fonts. However, it is possible to enter the "wax" value in the theme parameter of the wax_theme function to use other fonts. In this case, the fonts can be loaded like this:
```{r, eval=FALSE}
sysfonts::font_add_google(name = "Fira Sans", family = "fira-sans")
sysfonts::font_add_google(name = "Roboto Slab", family = "roboto-slab")

showtext::showtext_auto()
```
