---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

WaxTools
======

```{r, echo = F, warning = F, message = FALSE, include = FALSE}
knitr::opts_chunk$set(
  fig.path = "README_files/"
)
library(dplyr)

sysfonts::font_add_google(name = "Fira Sans", family = "fira-sans")
sysfonts::font_add_google(name = "Roboto Slab", family = "roboto-slab")

showtext::showtext_auto()

```

## Overview

`waxtools` is a package that brings together a set of useful day-to-day functions to facilitate work in the field of (mainly) ecology. It offers functions to clean up your datasets, customize your `ggplot2` graphs, check and correct the geometry of sf objects, create nice commented titles to separate scripts, and perform other specific tasks such as calculating cumulative specific richness, reformatting dates into a French format, etc. Thanks to the variety of its functions, `waxtools` can be used efficiently and conveniently in a variety of contexts and projects.


## Installation
```{r, eval=FALSE}
devtools::install_github("waxtiz/waxtools")
```

```{r, echo = F, warning = F, message = FALSE}
library(waxtools)
```
Then, load it.
```{r, eval = F}
library(waxtools)
```

## Usage

### The comment formatting function
Very simple function, but so useful in everyday life. Use it to segment your script with titles and subtitles, like h1, h2, h3... in html. Write your com() in the console, and the title will be put in your clipboard.

**The console part:**
```{r, eval = FALSE}
com("Project illustrating extremely well-organized code", heading = 1) # This is a H1
com("This section contains the loading of dependencies and datasets.", 2) # This is a H2
com("Let's get to work!", 2) # H2 again
com("First, let's clean up the dataset") # H3 (defaut value)
com("And let's visualize it:", 4) # H4 (etc.)

```

**All that's left to do is copy into the script:**
```{r, eval = F}
################################################################################
###                                                                          ###
###            Project illustrating extremely well-organized code            ###
###                                                                          ###
################################################################################

################################################################################
###     This section contains the loading of dependencies and datasets.      ###
################################################################################

library(dplyr)
library(ggplot2)
library(waxtools)

df_ori <- read.csv2("./input/data.csv")

################################################################################
###                            Let's get to work!                            ###
################################################################################

###################### First, let's clean up the dataset #######################

df <- df %>% clean_df()

                         #  And let's visualize it:  #

ggplot(df, aes(.....))+
    geom....


```

### WaxTheme
```{r, warning = F, cache = TRUE}
library(ggplot2)
library(waxtools)

ggplot(iris, aes(Sepal.Length, Petal.Length, color = Species)) +
  geom_point(size = 3) +
  labs(title = "Discrete color palette...",
       subtitle = "A subtitle",
       caption = "And finally, a caption text.") +
  theme_wax(theme = "wax") +
  scale_color_wax_d() # or scale_color_wax(discrete = T)

ggplot(iris, aes(Sepal.Length, Petal.Length, color = ..y..)) +
  geom_point(size = 3) +
  labs(title = "... or continuous",
       subtitle = "A subtitle",
       caption = "And finally, a caption text.") +
  theme_wax(theme = "wax") +
  scale_color_wax_c(name = "Petal Length") # or scale_color_wax(discrete = F)

```


### Calculate the cumulative taxonomic richness

```{r, cache = TRUE}
library(ggplot2)
library(waxtools)

result <- naturalist_df %>%
        calc_rich_sp("name", "date")

ggplot(result, aes(as.Date(date), cumulative_richness)) +
  geom_area(alpha = .75) +
  theme_wax()

```

### And more...
