---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

WaxTools
======

```{r echo=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_files/"
)

sysfonts::font_add_google(name = "Fira Sans", family = "fira-sans")
sysfonts::font_add_google(name = "Roboto Slab", family = "roboto-slab")

showtext::showtext_auto()
```

## Overview

`waxtools` is a package that brings together a set of useful and practical functions to facilitate work in the field, mainly, of ecology. It offers functions to customize `ggplot2` graphs, check and correct `sf` object geometry, create beautiful commented titles to separate scripts, and perform other specific tasks such as cleaning up data sets, calculating cumulative specific richness, etc. With its variety of functions, `waxtools` can be used effectively and conveniently in various contexts and projects.

## Installation
```{r eval=FALSE}
devtools::install_github("waxtiz/waxtools")
```

```{r}
library(waxtools)
```


## Usage

### waxtheme
```{r, warning = F}
library(ggplot2)
library(waxtools)


ggplot(iris, aes(Sepal.Length, Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "First, a chart title",
       subtitle = "Below, a subtitle",
       caption = "And finally, a caption text.") +
  theme_wax(theme = "wax") +
  scale_color_wax_d()

```

wax_theme uses by default the R fonts. However, it is possible to enter the "wax" value in the theme parameter of the wax_theme function to use other fonts. In this case, the fonts can be loaded like this:
```{r eval=FALSE}
sysfonts::font_add_google(name = "Fira Sans", family = "fira-sans")
sysfonts::font_add_google(name = "Roboto Slab", family = "roboto-slab")

showtext::showtext_auto()
```
